\documentclass[14pt,letterpaper]{book}
\usepackage{xunicode, setspace, xltxtra}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\renewcommand*\familydefault{\ttdefault}
\usepackage[T1]{fontenc}
\setlength{\parskip}{1.0em}
\setlength{\parindent}{0em}
\title{Black Mesa}
\author{Jared Whitehouse}
\date{2018/05/31}

\renewcommand*\contentsname{Table of Contents}
\begin{document}
\flushleft
\maketitle
\section{About the Story and the ideas that I am going to write}
\subsection{\textit{Characters}}
\begin{itemize}
\item The main Character
\par
\item A Security Guard.
\par
\item Other People and misc.
\end{itemize}

\section{About the characters.}
\subsection{The main Character}
\subsection{A Security Guard.}

About this \textit{``Security Guard''} is where The Main Character meets the Guard while the place is going to hell, and he is the one that is going to protect and teach the main character how to use a weapon and teaches him the main skills to survive and how to use a gun, Basic First Aid along with shooting and other nice things to learn while in the middle of a science experiment gone wrong situation. 

About the Guard
\\
I think that the age of the guy and I think hes going to be interesting to me and though.
Anyway lets write what this guy is going to be about\dots

\begin{itemize}
	\item Name: Ferdinand
	\item Age: 22
	\item Male
	\item He is pretty cute! 
\end{itemize}
 
\subsection{\textit{Other People and misc}}
\section{The Environment}
\textbf{\textit{What are the environment going to be?}}
\subsection{\textit{Settings}}

The setting of the story is going to be set at the \textit{`` Black Mesa Research Facility''}


Black Mesa is a research facility in the USA in New Mexico, in the middle of the desert. In the middle of the desert so you know that it is going to be really hot and stuff so bring a lot of water and some guns and ammo, including food because you don't want to get lost in the middle of the desert and this is going to be some good times while at the Black Mesa research facility where people do some science and some cool black projects that the government gives to Black Mesa so they can do their Teleportation technology and stuff\ldots 

I think this is going to be a great setting and also I am going to write more of this down here.. I think that i wrote them pretty well too and I just need to write even more though so i can get more work done for this story that i am writing\ldots Just some ideas that i might keep in the original thing. Like ``Authors Note's'' but the real thing at the start of the book\ldots so yeah. It's going to to be great!!
\subsection{\textit{Subsection For The Settings}}

I think that the settings in the environment are going to be hot to cold to night and day and mostly stuck in corridors and stuff like that\ldots and with a lot of guns and aliens from another universe so people are going to think that I am going crazy I think so yeah.

\textbf{add more things}
\subsection{\textit{Themes}}
There's going to be violence and a bunch of psychological things in the story that i am writing and you are reading right now, so there's going to be things that people are not  going to like and there might be some gay stuff etc\ldots Some love\ldots which i think I need more than anything.
\\
\tableofcontents
\section{The Beginning of the Story}
\chapter{Prologue}

% I think that instead of the classmates in the story I will put in a tour part in there.
\textbf{The start of all of this is going to change the world forever. There's not going to be a lot to come home to...}

"Okay, this is going to be really interesting!" I said to himself while packing up to get to his vehicle, He went downstairs to meet the rest of the group at the hotel lobby in New Mexico to go to the \textit{Black Mesa Research Facility}, This 'Research Facility' is a company where they get to do some the most important break troughs in cool things like, weapon technology to medicine, it is one great big thing of science and engineering at the Black Mesa Research Facility.

The tour comes out of the staff room and she says everyone's name one by one like in high school but more mature, She says my name ``Jared Whitehouse!" loud and clear, ``Here!" I say and she gives us the okay to the bus stop and we all get on board. The bus is open in a sense like you can put down your bag without any problems, like the Grey Hound buses that you get for long distance travel across the country, We all take our seats and the tour guide is going to talk about the things that we are going to see at the Black Mesa Research Facility today, which the date is today is June 10th 2017, as I open up my Journal to write something down what i am going to see today and I am going to log anything that i find interesting at the facility that I am going to see and or have anything interesting to say into my Journal. 

The tour guide tries to get my attention by snapping her fingers at me, then I look up quietly and I face towards her general direction, and she starts to speak into the mic while she explains what the research facility is all about, but then I ignore her because I have looked up a ton of stuff before going into this so I wasn't blind, also including that I like to learn things in depth so I can understand more than the normal civilian would know about this research/science facility. Including the things that they have done in conspiracy things like making teleportation devices to weapon development programs and other crazy things which are \textit{Out of this world!}

while spacing out for a little bit, I was going over the dam, the tour guide says ``This dam generates, 4 Billion kilo-watt hours in a day!" she said with some emphasis in her voice, I was surprised that I didn't know about that even though I studied the hell out of Black Mesa, oh well, what can I do... then we stop at a parking space where there are not many cars but I see some small houses in the back then I think to myself ``Oh, I think those are the living quarters for the people of Black Mesa\ldots", I go ask the tour guide about the houses in the back in the distance over there, ``Hey, What are those over there? are those living quarters for the people that work at Black Mesa?" The tour guide didn't hear what I said, then she doesn't bat an eye to me because she thinks that I am the one not paying attention to the tour and she doesn't really give a shit about me anyway, so I try to get in front of the line and I ask again to the `Tour Guide', ``Hey, ugh what are those over there? are those living quarters for the people that work at Black Mesa?", then she looks at me while we are going onto the train station, she looks at me with the death stare and she strikes the 'evil' cord on me, "Yes those are living quarters, anymore questions?" I nod 'no' politely and I move near the back of the crowd of people, one of the people are in the group said to me in a whisper "Yeah, She is a bitch, I don't like her. oh well" I laugh and he laughs also with me but she doesn't notice, so we board onto the train to head inside the Black Mesa Research Facility...

As we head inside the Facility, the place looked like it was in the middle of being made into some nice looking place for people to stay like at a 5 star hotel resort with marble front desk and the flooring was shiny and brand new like it was made yesterday, even though that half of the room was under construction, on one side of the room there completion and on the other side there was a mess of tools and people working on the floors and the walls, they looked like they were working for at least 12 hour shifts even though it was 9 in the morning, and people had their impressive looks on their face even though the room wasn't even done yet, but hey, this does look like a couple hundred thousand was spent on this room alone, funding from \textit{Uncle Sam} does help.

As we walk past the room that was being built for the lobby, we go down these some-what lavish hallways with nice shiny decor, there were some scientist talking about how this \textit{New Experiment} is not going to work and cause something of disaster, they went on and on about it, Then we are taking to the train station where the real thing is going to start\ldots ``Colour me impressed about these nice science labs that you have over here"

I said quietly to myself and the the Tour Guide said to me in some-what of a tone, ``Oh yeah, I think those are for show because the rest of the facility was made in the 1960's."

Yeah, I kinda knew about that even though that I was saying that sarcastically but she didn't care what I said, I roll my eyes as a turn around and we wait for the train to arrive at the station.

We all wait for the train, A security guard was running to the train station that we were waiting for, he comes up to me and says while he was out of breath ``I'm I late for the train it's suppose to come at 9:15!" I look at my watch and I said the time to him, ``The time is now 9:13" I smile at him with a cheery tone in my voice ``Hey At least you're not late for the train!" I giggle. The security guard laughs as I smile at him. ``Thanks for the time friend I think that you are my savour!" he smiles back at me.

The security guard gets scolded by this Tour Guide who isn't qualified to have the job, ``Hey boys you might wanna stop flirting and you might need yourselves another room!"

Me and the Security Guard both give her dirty looks while the train comes along to our stop, The door opens with swiftness.
``All aboard!" the tour guide says to the group with authority. We all get on board and take our seats,

I took the one in the very back so I can get a better look on the right side of the train, the Guard also sits right next to me. ``Hey it doesn't hurt to have a companion right?" He said with a nice calming voice, ``Yeah." I said back to him softly as I looked away nervously. ``My name is Ferdinand, what's yours?"

`Name's Jared, Jared Whitehouse, Nice to meet you. Ferdinand." The train started to move slowly out of the station and we began to move out and go deeper in the science facility. Also the idea of Ferdinand's name is quite interesting, I am thinking that he is from Europe, He doesn't sound like he has an English accent at all, its only the `American' pronunciation. ``Are you from Europe because your name does sound like it came from Germany?" I said to him with a curious look, he answered with no surprise the way that he acted he probably gets this all the time. ``Yeah my family is from Europe and they just wanted to keep the culture in my name so the family can keep its roots intact, I have no idea why they did that in the first place."

I didn't get surprised either I don't know why people like to keep their heritage in their family. But then people like to do that because they like to remember the past about how nice to was in the `good ol' days where people would their head cut off for saying something wrong that someone didn't like or stealing something small from a store, but then we live in a better time of secrecy and propaganda, Jared thought that the Soviets and the North Koreans did it best, but he knew that those places were fucked up and in a dystopia that's stuck into another time period, Does really made you think how the world is\ldots

The voice on the intercom was talking about the jobs that you can apply for, what the temperature is, in the imperial system anyway, because this is the place where they only get the use Fahrenheit.

Jared was thinking that does scientist have to learn both systems? \textit{(Celsius and Fahrenheit)} but why not learn one? because the rest of the world uses metric, it would make it easier but I think that did happen because it wasn't mandatory to use and learn the Metric system. Thanks to the government.

I turn my head towards Ferdinand and I say to him, ``Are the train rides here really boring, I usually find myself wondering." with sighness in my voice, his is what I expected ``Yeah, they are always boring, I wish that it could go a little bit faster, like a bullet train in Japan, those trains must hit at least 500kp/h!"

``I bet."
 
The train stops at next station the door opens on the train, the intercom with this weird robot voice said ``Please be-careful when leaving the train and check for your personal belongings and have a safe and productive day!", I get my personal belongings and I have all stuff, I get up and I wait for Ferdinand to move, Because he sat right next to me.

As we all get up from our seats and walk towards the front of the train to get off and get onto the metal grate, the grate looks like it was it was made 20 or 30 years ago when this place was made, the grate looked like it was really dangerous to walk on and could break at any moment, which was the scariest part of it. 

The tour guide makes us head into the entrance of this part of the facility and on the wall it was ``Sector C Laboratories'' and at one side there was A hallway with these stripes on the wall where it says ``Café, Armoury, Labs'', pretty interesting that they had the armoury have it apart of the tour, but we're here for science and shit, so why not show the armoury in the tour, 
 
I see Ferdinand walk to the hallway where there's a café and the armoury, I tried to get his attention by making a loud whistle sound with my fingers ``Hey Ferdinand! Why don't you introduce the armoury into the tour! I think that will be pretty bad-ass! What do you think about that!'' I spoken loudly so he is able to hear me across the room.
 
Everyone laughs in the lobby and it go silently after a few moments, Ferdinand agrees and the person in the front desk thought he was insane to let someone into the armoury without the supervisors permission, I think that they have visitor clearance for the people who has to have special permission, like investors and inspection officers, for the things that they need inspecting.

But me and Ferdinand went on our way and for some reason with all his trust that he had put into me on the first time we met, at a damn train station in a Research Facility out of nowhere, which I thought he was insane to do this kind of stuff in my mind but I kept my mouth shut because I thought this was the coolest thing that i have done in my life. Going to the armoury with the security guard while on tour.

While me and Ferdinand walk down to the armoury the power went out for 30 seconds while we were in the darkness then the emergency lights came on and some strange and some freaky red lighting along to go with the atmosphere, its creepy, I do like the dingy darkness of the most places because I always taught of the darkness always looked back at me and in nice and calming way.

Ferdinand went up into the control panel and took out his key-card swiftly out of his pocket and tapped on the door gently and the door unlocked with no problems. 

The guard of the other side of the door stopped us in our path and he wasn't looking too good with is frowned face and sagging eyes from his sockets, ``Hey, Me and my good ol' pal are going to take a tour of the armoury its apart of the schedule here." I smiled at the man who wanted to stop our interesting yet exciting tour of the Black Mesa Research Facility.

``I am not going to let you in here ever again with a civilian unless they are here for important reasons! You got that, I will not be giving you any favours \textit{anymore!} Ferdinand.

A second officer to his right gave me a badge that was written \textit{``CIVILIAN}, I looked at badge that they gave me and it looked very plain and it looked like the font was on the front cover from an 90s Time's Magazine but without me on the cover, What a shame that is.

Ferdinand showed me around the armoury there was a firing range to the left and at the right there were the locker rooms and in front was the weapons stored there along with extra security on the side, and Ferdinand said that there are automatic rifles in there, but not anymore they moved it somewhere else so the rookies can't get their hands on because there are some problems with the rookies would get frisky with these weapons.

We first take a look at the shooting range, no ones there at the moment because everyone is on duty trying to keep this place safe. unless something bad is going to happen.

\textit{maybe or something is \textbf{`really!'} bad is going to happen}

Ferdinand looks at the shooting range and he nods at me with the emotion that he wants to go in and squeeze in a few rounds in the range, I nod at him with a shady grin with the intent that `I' Want to put in some rounds into the range.

The power comes on suddenly, so that was convenient. I thought to myself.

He goes to the armoury window and asks `The Man' with all the guns on the other side of the military grade weaponry, Even though that I have no idea whats on the other side. its properly just full with 9mm pistols along with ammo and magazines, but I like to think big, instead I am thinking about crazy things because I think I took my medication this morning. \small{\textit{(Zoloft of course.)}}

Ferdinand walks slowly towards me with the same emotion that he had on his face as we had when we first wanted to go to the firing range.

We both walk into the firing range, we go to the 5 aisle of the range, he put the Glock down on the range table, he put the magazine in one hand, and a box full with 9mm rounds in it. It must of had more than 200 of them in there. in his right, were one 9mm round in his index, middle and thumb for maximum grip.

He put one into the magazine, *Click* with the same motion from his hand and grip, *Click, click click.*
In a matter of less than 10 seconds Ferdinand filled up the entire magazine, it was amazing and ecstatic. some what purifying in a way. with gunpowder and metal, Ferdinand has a Glock in one hand instead of the 9mm rounds, in the left hand had the filled up and loaded magazine instead of an empty one, he put the magazine in the butt of the gun and the sliding sound of the metal being loaded into the sound and the rail of the Glock was in a unloaded state then he moved his left hand over the top of it and he pulled it backward and let go a big loud metallic click.

Ferdinand said to me, ``Are you ready for the first round?"

``Yeah, Let's do it." I replied with a nervous tone.

He takes one shot and said with a dubious look at his face ``Whoa, That was awesome!"

The power goes out and and goes completely black along with the emergency lights out there were explosions in the distance and everyone stood still, shocked to find out something is happening, then, the unsettling klaxon on the intercom was now phrasing the following sentence...

\large\textbf{\textit{``Warning, unknown specimen found in Sector C, B Laboratories, Warning Fire Hazard in Sector C, Warning multiple causality in Sector C test labs."}}

\par


\textbf{\emph{Now, this is where everything is going to change. forever...}}

\chapter{Unforeseen Consequences}
The lights went out after a few moments. then somebody started screaming and yelling, 

Then there were explosions outside of the room right next to us. It was an impossible feeling and I stood frozen for a second then Ferdinand told me to run into the room that he was just in to get the armour, ammunition, and of course a gun.

So I ran in there as quickly as I can, I got the gun, amour a helmet and ammunition for the pistol that I found in the armoury, it was the same as Ferdinand's, it had a matte finish with some white colour on the iron sights of the pistol. I had a weird feeling about holding this weapon, because I have never held one before, Not even counting that I shot one before...


I jogged towards Ferdinand and something happened like he was frightened... "I think that, I saw someone get their head got jumped on or something, His head started to bleed, There was something or an alien that jumped on his skull and coupled with his head. and now hes on the ground, lying there..."


I looked over the security booth where his so-called boss was there to check who comes and who leaves, I lean over to see that there was really an alien on top of his head, I jumped backwards with a frighten look on my face. "Oh, shit! That guy is not moving and he looks like his entire head is bleeding, the alien is also looks like he is sucking all the blood from his face!" I tremble with fears that something is going to happen, I think that I am going to die today, but I am not going to let that happen, I put my face onto Ferdinand chest, "We are going to be alright, you are with me right now" he said softly while he was patting me on the head


He wanted to make me feel better by giving me insights that I am going to get out of this facility, even though that there are going to be bigger problems down the road if this, 'Disaster' doesn't go to the mainstream media where I might have to be interviewed, I do not like those because they're made to make money off of these, Disasters and other fucked up things that they have to do to get some money.

I started to calm down, my heart rate is slowing, "Thank you Ferdinand, you are the person that I have ever met... Thank you." I said softly to him because he understands what it means to be in this kind of danger, security guards don't really have to deal with criminals, but he has dealt with this kind of stuff before, I think... "Ferdinand, you look so calm? How are you so calm while in a dangerous situation's Ferdinand?" I asked him with a worrying voice to him. He responded with "Once I was an Officer that had to deal with a lot of stress at work, there isn't a lot that I can go on right now because we need to get out of here." I nodded we got all of the things that we had including weapons and water, no food, that's one problem that can be fixed soon if there is a café in the facility or at least a snack machine. Ferdinand and I started to run out of the room and there were a lot of broken equipment everywhere. We run to the main lobby where the tour guide including the group that I was in. "Hello! is anyone there?" I yell in the lobby because It was completely silent, it was a bit too quiet because this place was busy like a train station in New York City there were scientist going to their labs to go to work, people on the intercom talking about people being summoned to their workplaces and or meetings about secret things that they like to do behind our backs.
Ferdinand also yelled "Hello!" just to get some attention so anyone can hear us. then there were nothing, just silence. "Oh my god where the hell is everyone?" I questioned to myself. "I have no idea man, I think that there they went down to the labs or something. we should check the offices just so anyone is okay, I think that is a good plan." Ferdinand said with an objective in mind. "Yeah, let's go." I said. off we went to the office complex next to the laboratories. as we were running towards the office complex the corridor was flickering with some electrified sparks in the light bulbs in the ceiling, there were these scientist, they were covered in blood. their heads, looked like they were gone. but they were standing. and walking slowly, their body twisted towards us. I can see \textit{barley} in the dark corridor, Ferdinand looks at me frightened, I looked at him, "Are you okay? Do you see those people at the other end of the corridor? I think they are still alive."


"No!" he yelled at me,


"Do you see the those sharp-like claws on them?" he asked me while he whispered at me.
"I think I do. this is fucking insane, who are they..." I asked to myself,
"I don't know, Let's keep moving." he said quietly...


We both moved slowly down the hallway, the hallway was cold and no so humid. The air was dry. we were getting closer to these 'scientists', these scientists looked dis-formed, their laboratory coat's were on the body where and covered in blood, their heads weren't on their body but there was this, crab looking creature on their heads, the torso looked like it had a giant mouth to the chest cavity to the intestine area. it looked like it came from a monsters laboratory or even a Stephen King Novel.


As we got to the end of the end of the corridor, we were relived as we stood up slowly we brushed off the sweat off of our faces, "That was scary has hell." I said, "Sure is" Ferdinand looked great for the things that we just saw.


We walked down the hallway, we gripped how pistols and Ferdinand turned the safety off and he had his index finger on the trigger.

I do the same because I think that something is going to happen, the atmosphere has heightened to the point that we started to move nice and slowly so we can get to the office complex, There were some of the same monsters that we have seen in the other corridor that we just sneaked across, Ferdinand held up his gun so he can \textit{'speak'} to these creatures... 

"Hey! who are you!" he spoke to the strange creatures that we saw in the science uniforms.
They didn't say anything, they moved towards Ferdinand and I then one of their long nails are look incredibly sharp that it could do some devastating damage. The humanoid creature took a strong whip to Ferdinand, He dodged the hit from the creature and he took a shot at the creature and it didn't go down so it didn't took one, two, three shots.


"Oh Fuck. That is fucking scary, okay when you see one of these 'things' damn it we should call these things zombies. because they act like it!" Ferdinand spoke with a tremble in is pronunciation 


"Yeah we should, zombies!" I said to Ferdinand.


"Also you should of helped me with that! man that is not cool!" he spoke with a tone in his voice, He wasn't happy about it, but I am kind of afraid of shooting a gun because I have never shot one, but over here in America, They say \textit{"There is always a first time"}, "I am sorry, I just froze up..."


"Oh, yeah that's your excuse, oh well, this is what we have. me and you. come one let's keep on moving." he turned away from me and moved on with his stance position where he was in a tactical stance where he was ready for anything, so I do the same, we were getting close to the laboratories and the next section of the complex, as we got to the door there was a metal bar or a iron pipe, it looked like it was a baton that a officer would use to hit a drug dealer who was going a bit crazy, it wasn't black like the nightstick that they have, it had a metallic look with a nice shiny, on the end of the iron pipe was some blood that looked like it started to dry like a scab on a cut on a piece of skin, Ferdinand picked up the iron pipe and tossed it towards me and I caught it with some grip and it almost slid out of my hands because the pipe weighted a hefty of a couple of kilograms.


"Thanks." I said with some politeness


"No problem, can you break open that door because it looks completely shut on both sides." he said with a commitment in his voice.
I walked up to the broken door that had a huge piece of concrete from the supports of the building.
The bottom of the window didn't seemed to be broken so I took the iron rod and with one hit.

\textbf{*SMASH*}

the glass went everywhere and there were some small shards of glass on my flannel shirt and some on my lightweight body-armour, this thing is quiet a heavy lift on my torso, I swiped the shards off and Ferdinand crept over and he started to go in first and I had my handgun pointed down the corridor where we once came from.

"It's okay we can move now." said Ferdinand on the other side of the broken door to get into the laboratories, so I crouched down and I tried not to cut myself on the broken window that I smashed. "Don t touch the glass." I said to myself while I was going through to the door, I got through without cutting or injuring myself.

Ferdinand helped me to get me up on my feet and we both kept on moving through the laboratories, the science laboratories are quiet interesting because it isn't really like the things that you would see in high school, not like the test tubes or any of those kind of beginner type stuff, but there were a bunch of things that were written on the whiteboard like mathematical problems along some-what expensive equipment that they use for science experiments that they conducted which I have no understanding of what they were doing, the lights seemed on this sector of this place because the rest of the place seemed like they have backup generators but I don't understand why they don't have that kind of stuff in the lobby because they don't want to spend too much time on things like that. but the laboratories seem to be nice and clean despite the things that we have seen in the other part of the facility had to offer like blood and gore and the aliens, zombies that were wondering this place. like zombies... but I think there are more aliens that came out of here.

We walked slowly down the hallway of the laboratories there isn't really much, but there's some other things that are really strange like theres a bunch of glass on the ground and there are some blood with a trail to the other side of the lab. it looks like this person or something bled so much that it died but it was red like red wine, nothing out of the ordinary because this is human blood \textit{hopefully.}
"Hey takes take a look at this room Ferdinand, this might have someone or some supply's for us, I am not sure." 

"Yeah I think that theres something in there, we should take a look and see... Just be careful." as we got to the door, the door open automatically as we gotten close to it.

"Damn automatic doors. they kinda freak me out, I don't know why though." I said to myself, as we both walked into the room with some skepticism because of the things that we have seen so far that we don't know about.

We looked through the laboratory to see if we can find anything to medical supply's and other nice things that we have to survive through this madness. We both looked through desk drawers, computers because why not, filing cabinets closets and other things that we can get, as I was looking through the lab I found a couple of tools, medical kits it looks full with gauss, antibiotics so we don't die from infection. this is the thing that some people need to get to survive.

Ferdinand looked around and took a look in the medical kit because something caught his eye, there was a key in there and on the key-ring there is a label on it said "Safe Key", "This is interesting, we should look for this safe because I don't know why A lab scientist would hide a key or a safe in their lab?" He asked me but I had no idea what to say so i decided not to say anything about that nor I didn't know about these kinds of things. I took this somewhat heavy medical kit that we just found and the safe that we are going to have to find now. and I hope nothing is really bad about this part of the facility.


As we got out of simple laboratory the lights started to flicker then the corridor went dark and the lights went up again with some dimming, and shortage in the circuits. "I think we should keep on moving but be careful friend, we don't want to die just yet." he said to me with a nice and calming without stresses in his tone of voice, While saying that he is very calming in the part of a disaster, which is my favourite part Ferdinand's character.


I started to look around the other laboratories through the windows because we could use something in there because of the medical that we just found even though that i am not sure where the other people are. or they are dead hopefully not. but our shoes on the floor started to make welching sounds because the blood that's on the floor that seemed to be fresh, the blood on the floor started to smear  on the floor and making footprints, "Ugh, this blood, fresh. Really Fresh!" I spoke with disgust and trying not to slip on it. it was quite disgusting. I didn't want to look at the ground so i don't have to slip and fall on the ground and get covered in blood. "I do not want to slip and fall in this... disgusting.", "Yeah me too" Ferdinand agreed with me. as we walked towards the room where this blood trail is leading us into a very darkened room where there was a monitor that was flickering in one part of the laboratory and a dim red tinting to it because of the hazard lights including the emergency power generators were on. we got towards the strobing light that is on the other side of the room and there was an office chair in front of the strobing light and it wasn't facing towards me and Ferdinand. the tension was getting higher because the stink coming from the corner of the room smelt rotten, it smelt worse than rotten eggs with a sour milk combination, it was one of the worst things that you could smell.

We went closer and we were able to reach at arms length, we went a bit closer and we both looked at each other and we both agreed to turn around the chair, as soon as we did there was a rotting dead corpse in the chair and there was to look like a face-hugger was eating his face, we both jumped back and screamed and we started to shoot at the creature that was eating the corpses face, I started shooting at it first because it was one of those moments where you find something so dangerous that we have to fight or flight, so I decided to kill it with my Glock that Ferdinand gave to me while we were back in the armoury. the creature fell down as we put 3 shots into the thing and it slid off like a dead rabbit of some sort and I think that it was one of the most freakiest thing that I have seen in my life. It appeared that It looked like a crab with small black eyes in-front of the creature and at he bottom there were these beaked fangs along a huge crater in the middle of the thing to make it couple with the head of the host so they can control them so they can turn into zombies, or something so once the human body  is done, or at least the host body is rotten and all of the nutrition is gone from the body it goes to another body and so on, so this is the most fucked up thing in the world and I don't know how these things are going to be easy to fight with, I thought in my head that we just have to shoot em' because That is the only thing that I have been thinking this entire time. just kill them all but this just came within the second in my mind, It kinda a revelation because this is how I am going to realize if I am not going to hurry and not waste my time, I might end up like this guy in a goddamn chair dead while a face-hugger is sucking out my eyes... So I think that is this one of the real reasons why I am not going to die right now. I have to get out and write a research paper on the way out the door. but this is so significant would that even help me get credit as a writer in the field that I am writing now for this travel guide to New Mexico? I don't think so, it might kill me in the long run anyway, as the task at hand... Me and also Ferdinand was shocked and horrified at the situation and we needed to get out of here as fast as possible because those gunshots were so loud that after a few seconds we could hear them coming slowly and steadily, that is kinda the worst part because when you're trapped you're trapped and you cannot get out.

Ferdinand tapped my shoulder hard, "Come one we gotta go right now! I can hear them coming, follow me lets go to the office complex because theres going to be a lot of them and if we don't get out of here as fast as possible we are not going to make it!!" he yelled at me and we both ran out of the room at full speed, as got out of the room and we didn't notice the blood and we almost fell into the blood and there were some of those face-hugger alien things coming round the corner, we ran really quickly down the corridors trying not to slip and fall on the shiny slippery floor, Where is th- office complex, damn it!" I panted, "Over here!" Ferdinand yelled.

there is a sign on the ceiling and it said 'Office Complex', and we ran down that hallway and there was an elevator and we both ran in there and we tried to press all the buttons that there was avaliable on there. "oh, thank god, we are good, for now." I said, 

Git initalized






\end{document}
